---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# epoxy

<!-- badges: start -->
<!-- badges: end -->

epoxy makes [glue] easy to use in R Markdown documents.

_epoxy is in a proof-of-concept stage right now._
_I'm still experimenting, so the API ~~may~~ will change._
_I'd love to hear your thoughts, feel free to [open issues](https://github.com/gadenbuie/epoxy/issues)_.

## Installation

You can install the proof-of-concept version of epoxy with [remotes].

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("gadenbuie/epoxy")
```

## Example

```{r library-epoxy}
library(epoxy)
```

Loading epoxy adds a new chunk type called `glue`.

### glue chunks

You can write regular markdown in the `glue` chunk,
wrapping any R expressions in `{...}`,
just like in `glue::glue()`.

````
```{glue}`r ''`
The average speed of the cars was **{mean(cars$speed)} mph.**
But on average the distance travelled was only _{mean(cars$dist)}_.
```
````

```{glue}
The average speed of the cars was **{mean(cars$speed)} mph**.
But on average the distance travelled was only _{mean(cars$dist)} ft_.
```

All of the arguments of `glue::glue()` are available as chunk options,
so you can configure the `.open` and `.close` characters,
e.g. `{{` instead of `{`,
among other options.

With an amazing stroke of luck,
RStudio autocompletion works inside `glue` chunks!

### Style replaced values

You can use the `expoxy_style_wrap()` with the `.transformer` chunk option
to wrap the evaluated R expression in formating or templating text.
Or you can use the pre-set 
`epoxy_style_bold()`, `epoxy_style_italic()`, or `epoxy_style_code()`
style transformers.

````
```{glue, .transformer = epoxy_style_bold()}`r ''`
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$speed)}
```
````

```{glue, .transformer = epoxy_style_bold()}
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$dist)} mph.
```

### glue chunks are vectorized

Unlike inline R code, the `glue` chunks are vectorized.
This can be something to watch out for or it can be an advantage:

````
```{glue}`r ''`
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```
````

```{glue}
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```

You can collapse fields automatically using the `epoxy_style_collapse()` transformer.
You can then choose how vectors are collapsed by adding `*`, `&` or `|` 
to the end of the expression.

- `*` collapses with commas, e.g. `{letters[1:3]*}`.
- `&` collapses with commas and adds `" and "` between the last two items
- `|` collapses with commas and adds `" or "` between the last two items.

````
```{glue, .transformer = epoxy_style_collapse()}`r ''`
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```
````

```{glue, .transformer = epoxy_style_collapse()}
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```

You can change the separator between entries and between the last entry
using the `sep`, `last` and the `_and` and `_or` specific arguments
of the `epoxy_style_collapse()` function.

### Templating with glue chunks

It's also possible to create a reusable template.
Use the `ref.label` chunk option to reuse a template 
using the values in the `data` chunk option,
which can be a list or data frame.

```{r}
mpg <- data.frame(
  manufacturer = c("Chevrolet", "Dodge", "Ford"),
  model = c("Malibu", "Caravan", "Expedition"),
  cty = c(19, 7, 11),
  hwy = c(27, 24, 17)
)
```

````
```{glue car-name, eval=FALSE}`r ''`
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{glue ref.label="car-name", data = mpg}`r ''`
```
````

```{glue car-name, eval=FALSE}
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{glue ref.label="car-name", data = mpg}
```

## Whisker Engine

Sometimes the `glue` engine doesn't quite deliver the template power you need.
In these cases, you can use the `whisker` engine instead.

````
```{r}`r ''`
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}`r ''`
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```
````

```{r}
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```

## Raw Blocks

### HTML Blocks

Use the `glue_html` block to glue R and HTML together.
The output is [raw HTML](https://pandoc.org/MANUAL.html#raw-htmltex).
By default, expressions in these types of blocks are wrapped in `{{` and `}}`,
like whisker templates above.

````
<ul>
```{glue_html, data = mpg}`r ''`
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>
````

<ul>
```{glue_html, data = mpg}
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>

### LaTeX Blocks

Similarly, you can also use `glue_latex` blocks to glue R and LaTeX together.
By default, expressions in these types of blocks are wrapped in `<` and `>`.

````
\begin{itemize}
```{glue_latex, data = mpg}`r ''`
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````

In R Markdown knitting into a LaTeX output,
this renders as:

````
\begin{itemize}
```{glue, data = mpg, .open = "<", .close = ">"}
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````

[glue]: https://glue.tidyverse.org
[remotes]: https://remotes.r-lib.org
