---
title: "epoxy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{epoxy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

```{r child = "../man/fragments/installation.Rmd"}
```

## Setup

```{r child = "../man/fragments/setup.Rmd"}
```

## Use epoxy

```{r child = "../man/fragments/first-example.Rmd"}
```

## Inline styles

**epoxy** provides inline styling inspired by
[cli's inline markup](https://cli.r-lib.org/reference/inline-markup.html).
This styling is enabled by default in `epoxy()`, `epoxy_html()` and `epoxy_latex()`
and their respective knitr chunk engines.

Here's an example using a small list containing data about a movie.

```{r}
movie <- list(
  year = 1989,
  title = "Back to the Future Part II",
  budget = 4e+07,
  domgross = 118450002,
  imdb_rating = 7.8,
  actors = c(
    "Michael J. Fox",
    "Christopher Lloyd",
    "Lea Thompson",
    "Thomas F. Wilson"
  ),
  runtime = 108L
)
```

We can use the inline styles to format the replacement text
as we build up a description from this data.

````{verbatim}
```{epoxy echo = FALSE}
The movie {.emph {.titlecase movie$title}}
was released in {.strong movie$year}.
It earned {.dollar movie$domgross}
with a budget of {.dollar movie$budget},
and it features movie stars
{.and movie$actors}.
```
````

```{epoxy inline-movie-first, echo = FALSE}
The movie {.emph {.titlecase movie$title}}
was released in {.strong movie$year}.
It earned {.dollar movie$domgross}
with a budget of {.dollar movie$budget},
and it features movie stars
{.and movie$actors}.
```

Read more about inline styles in `?epoxy_style_inline`.

### Style replaced values

You can use the `epoxy_style_wrap()` with the `epoxy_style` chunk option
to wrap the evaluated R expression in formatting or templating text.
Or you can use the pre-set
`epoxy_style_bold()`, `epoxy_style_italic()`, or `epoxy_style_code()`
style transformers or with `epoxy_style()`.

````
```{epoxy, epoxy_style = epoxy_style("bold")}`r ''`
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$speed)}
```
````

```{epoxy, epoxy_style = epoxy_style("bold")}
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$dist)} mph.
```

### epoxy chunks are vectorized

Unlike inline R code, the `epoxy` chunks are vectorized.
This can be something to watch out for or it can be an advantage:

````
```{epoxy}`r ''`
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```
````

```{epoxy}
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```

You can collapse fields automatically using the `epoxy_style_collapse()` transformer.
You can then choose how vectors are collapsed by adding `*`, `&` or `|`
to the end of the expression.

- `*` collapses with commas, e.g. `{letters[1:3]*}`.
- `&` collapses with commas and adds `" and "` between the last two items
- `|` collapses with commas and adds `" or "` between the last two items.

````
```{epoxy, epoxy_style = epoxy_style("collapse")}`r ''`
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```
````

```{epoxy, epoxy_style = epoxy_style("collapse")}
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```

You can change the separator between entries and between the last entry
using the `sep`, `last` and the `_and` and `_or` specific arguments
of the `epoxy_style_collapse()` function.

### Templating with epoxy chunks

It's also possible to create a reusable template.
Use the `ref.label` chunk option to reuse a template
using the values in the `data` chunk option,
which can be a list or data frame.

```{r}
mpg <- data.frame(
  manufacturer = c("Chevrolet", "Dodge", "Ford"),
  model = c("Malibu", "Caravan", "Expedition"),
  cty = c(19, 7, 11),
  hwy = c(27, 24, 17)
)
```

````
```{epoxy car-name, eval=FALSE}`r ''`
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{epoxy ref.label="car-name", data = mpg}`r ''`
```
````

```{epoxy car-name, eval=FALSE}
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{epoxy ref.label="car-name", data = mpg}
```

## Whisker Engine

Sometimes the `epoxy` engine doesn't quite deliver the template power you need.
In these cases, you can use the `whisker` engine instead.

````
```{r}`r ''`
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}`r ''`
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```
````

```{r}
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```

## Raw Blocks

### HTML Blocks

Use the `epoxy_html` block to epoxy (glue) R and HTML together.
The output is [raw HTML](https://pandoc.org/MANUAL.html#raw-htmltex).
By default, expressions in these types of blocks are wrapped in `{{` and `}}`,
like whisker templates above.

````
<ul>
```{epoxy_html, data = mpg}`r ''`
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>
````

<ul>
```{epoxy_html, data = mpg}
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>

### LaTeX Blocks

Similarly, you can also use `epoxy_latex` blocks to epoxy R and LaTeX together.
By default, expressions in these types of blocks are wrapped in `<` and `>`.

````
\begin{itemize}
```{epoxy_latex, data = mpg}`r ''`
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````

In R Markdown knitting into a LaTeX output,
this renders as:

````
\begin{itemize}
```{epoxy, data = mpg, .open = "<", .close = ">"}
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````
