---
title: "epoxy in Reports"
output: 
  cleanrmd::html_document_clean:
    theme: new.css
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{epoxy in Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = "#>"
)
```

[glue]: https://glue.tidyverse.org

## Setup

```{r child = "../man/fragments/setup.Rmd"}
```

## Using epoxy chunks

```{r child = "../man/fragments/first-example.Rmd"}
```

## Inline styles

**epoxy** provides inline styling inspired by
[cli's inline markup](https://cli.r-lib.org/reference/inline-markup.html).
This styling is enabled by default in `epoxy()`, `epoxy_html()` and `epoxy_latex()`
and their respective knitr chunk engines.

```{r child = "../man/fragments/example-movie.Rmd"}
```

Read more about inline styles in `?epoxy_style_inline`.

### Style replaced values

You can use the `epoxy_style_wrap()` with the `epoxy_style` chunk option
to wrap the evaluated R expression in formatting or templating text.
Or you can use the pre-set
`epoxy_style_bold()`, `epoxy_style_italic()`, or `epoxy_style_code()`
style transformers or with `epoxy_style()`.

````
```{epoxy, epoxy_style = epoxy_style("bold")}`r ''`
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$speed)}
```
````

```{epoxy, epoxy_style = epoxy_style("bold")}
All cars stopped between {min(cars$dist)} and {max(cars$dist)} feet
from a starting speed of {min(cars$speed)}---{max(cars$dist)} mph.
```

### epoxy chunks are vectorized

Unlike inline R code, the `epoxy` chunks are vectorized.
This can be something to watch out for or it can be an advantage:

````
```{epoxy}`r ''`
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```
````

```{epoxy}
{1:4}. "{letters[1:4]}" is for {c("apple", "banana", "coconut", "donut")}
```

You can collapse fields automatically using the `epoxy_style_collapse()` transformer.
You can then choose how vectors are collapsed by adding `*`, `&` or `|`
to the end of the expression.

- `*` collapses with commas, e.g. `{letters[1:3]*}`.
- `&` collapses with commas and adds `" and "` between the last two items
- `|` collapses with commas and adds `" or "` between the last two items.

````
```{epoxy, epoxy_style = epoxy_style("collapse")}`r ''`
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```
````

```{epoxy, epoxy_style = epoxy_style("collapse")}
- The first three letters are {letters[1:3]*}.
- When capitalized, they are {LETTERS[1:3]&}.
- They're indexed by {1:3|}.
```

You can change the separator between entries and between the last entry
using the `sep`, `last` and the `_and` and `_or` specific arguments
of the `epoxy_style_collapse()` function.

### Templating with epoxy chunks

It's also possible to create a reusable template.
Use the `ref.label` chunk option to reuse a template
using the values in the `data` chunk option,
which can be a list or data frame.

```{r}
mpg <- data.frame(
	manufacturer = c("Chevrolet", "Dodge", "Ford"),
	model = c("Malibu", "Caravan", "Expedition"),
	cty = c(19, 7, 11),
	hwy = c(27, 24, 17)
)
```

````
```{epoxy car-name, eval=FALSE}`r ''`
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{epoxy ref.label="car-name", data = mpg}`r ''`
```
````

```{epoxy car-name, eval=FALSE}
- A {manufacturer} {model} gets {cty} city and {hwy} highway miles per gallon.
```

```{epoxy ref.label="car-name", data = mpg}
```

## Whisker engine

Sometimes the `epoxy` engine doesn't quite deliver the template power you need.
In these cases, you can use the `whisker` engine instead.

````
```{r}`r ''`
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}`r ''`
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```
````

```{r}
contestant <- list(name = "R User", value = 1000, taxed = 600, in_ca = TRUE)
```

```{whisker data = contestant, echo=FALSE}
Hello {{name}}:
You have just won ${{value}}!
{{#in_ca}}
Well, ${{taxed}}, after taxes.
{{/in_ca}}
```

## HTML and LaTeX chunks

### Markdown chunks

The `epoxy` chunk engine can be used in any output format.
In practice, it works best in markdown 
(i.e. generally in R Markdown or Quarto)

````{verbatim}
```{epoxy, data = mpg}
- **{manufacturer}** _{model}_
```
````

where it renders as:

````
```{epoxy, data = mpg}
- **{manufacturer}** _{model}_
```
````

If you're writing for an HTML or LaTeX output, however,
you may need to write literal HTML or LaTeX in your document.
With the `epoxy` chun,
you'd need to escape any `{` or `}` in your text by doubling them,
otherwise the content within will be treated as a template expression.
To avoid this friction,
epoxy provides two additional chunk engines,
`epoxy_html` for writing raw HTML
and `epoxy_latex` for writing raw LaTeX.

### Raw HTML chunks

Use the `epoxy_html` block to epoxy (glue) R and HTML together.
The output is [raw HTML](https://pandoc.org/MANUAL.html#raw-htmltex).
By default, expressions in these types of blocks are wrapped in `{{` and `}}`,
like whisker templates above.

````{verbatim}
<ul>
```{epoxy_html, data = mpg}
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>
````

````
<ul>
```{epoxy_html, data = mpg}
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>
````

Notice that the output is HTML but wrapped in a
[pandoc raw html block](https://pandoc.org/MANUAL.html#extension-raw_attribute),
which tells pandoc that the content is HTML that shouldn't be modified[^raw-html].
It also means that the output of the chunk will 
[only be included in HTML documents](https://bookdown.org/yihui/rmarkdown-cookbook/raw-content.html).

If your `epoxy_html` block is contained within another a raw html block,
or if you want to force the output to appear,
you can set the chunk option `html_raw = FALSE`.

[^raw-html]: Without the raw html block, pandoc can do unexpected things to HTML, even if your output is HTML-friendly. If you are explicitly writing HTML markup in your R Markdown or Quarto document, you should probably wrap that markup in an `{=html}` block.

`````{verbatim}
````{=html}
<ul>
```{epoxy_html, data = mpg, html_raw = FALSE}
  <li><strong>{{manufacturer}}</strong> <em>{{model}}</em></li>
```
</ul>
````
`````

`epoxy_html` uses two custom transformers,
`epoxy_style_inline()` and `epoxy_style_html()`,
applying the html style before the inline formatting style.
With `epoxy_style_html()` you can use `element.class#id` syntax
to wrap expressions in HTML elements (all parts are optional).
Let's use this syntax to place manufacturer and model in
`<strong>` and `<em>` elements,
each with a custom class.

````{verbatim}
<ul>
```{epoxy_html, data = mpg}
  <li>
    {{strong.car-make manufacturer}}
    {{em.car-model model}}
  </li>
```
</ul>
````

````
<ul>
```{epoxy_html, data = mpg}
  <li>
    {{strong.car-make manufacturer}}
    {{em.car-model model}}
  </li>
```
</ul>
````

Because `epoxy_style_html()` is applied first,
`{{.uppercase manufacturer}}` is assumed to be a CSS class
and not an inline style class.

````{verbatim}
```{epoxy_html data = mpg[1,]}
{{.uppercase manufacturer}}
```
````

````
```{epoxy_html data = mpg[1,]}
{{.uppercase manufacturer}}
```
````

You can get access the inline formatter by adding one additional layer of `{{ }}`.

````{verbatim}
```{epoxy_html data = mpg[1,]}
{{span {{.uppercase manufacturer}} }}
```
````

````
```{epoxy_html data = mpg[1,]}
{{span {{.uppercase manufacturer}} }}
```
````

This works even if you don't use the HTML formatter.
In the last example,
`{{ {{.uppercase manufacturer }} }}` would produce `CHEVROLET`.

### Raw LaTeX chunks

Similarly, you can also use `epoxy_latex` chunks to epoxy R and LaTeX together.
By default, expressions in these types of chunks are wrapped in `<` and `>`.

````{verbatim}
\begin{itemize}
```{epoxy_latex, data = mpg}
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````

In R Markdown knitting into a LaTeX output,
this renders as:

````
\begin{itemize}
```{epoxy_latex, data = mpg}
\item \textbf{<manufacturer>} \textit{<model>} gets <cty> city and <hwy> highway miles per gallon.
```
\end{itemize}
````

Note that, like `epoxy_html` chunks,
`epoxy_latex` places the output in 
[raw latex blocks]( https://bookdown.org/yihui/rmarkdown-cookbook/raw-latex.html).
This behavior can be disabled by setting the chunk option
`latex_raw = FALSE`.
