---
title: "Inline Reporting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inline Reporting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[knitr]: https://yihui.org/knitr/
[tj-lists]: https://www.tjmahr.com/lists-knitr-secret-weapon/

```{r, include = FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = "#>"
)

emo_ji <- function(...) {
	"&#x1F606;"
}
```

```{css echo=FALSE}
.epoxy-output {
	border-left: 2px solid var(--bs-primary, #0b535d);
	padding: 1em;
	margin-bottom: 1.5em;
}
.epoxy-output > :last-child {
  margin-bottom: 0;
}
```

```{r setup, include = FALSE}
library(epoxy)
```

This vignette is heavily inspired by
[Tristan Mahr](https://www.tjmahr.com/)'s post
[_Lists are my secret weapon for reporting stats with knitr_][tj-lists].
Please read his original for an excellent introduction
on how to better organize your data for inline reporting scenarios with lists.
I'm going to borrow several examples directly from that post.

## Plug-in reporting

```{r ref.label="orange-summary-stats", eval = TRUE, echo = FALSE}
```

Both Tristan and Yihui Xie call _inline reporting_
the act of interleaving R expressions in the prose of markdown text.
When you click the **Knit** button or call `rmarkdown::render()`
to build your report,
`knitr` evaluates these R expressions, 
turns them into text and plugs them into your output.

The most common use case is for reporting descriptive statistics.
To illustrate, I'll use the [`Orange` dataset](https://rdrr.io/r/datasets/Orange.html)
which contains circumference measurements of 
```{epoxy}
{n_trees} orange trees at {n_timepoints} points in time.
```

Here is some R code we might use to summarize the `Orange` data:

```{r orange-summary-stats}
n_trees <- length(levels(Orange$Tree))
n_timepoints <- length(unique(Orange$age))
```

And here are some lines we might include in a report about the growth of these trees:

````{verbatim}
```{r setup, include = FALSE}
library(epoxy)
```

```{epoxy}
The dataset contains {nrow(Orange)} tree size measurements
from {n_trees} trees at {n_timepoints} time points in the study.
```
````

::: epoxy-output
```{epoxy echo=FALSE}
The dataset contains {nrow(Orange)} tree size measurements
from {n_trees} trees at {n_timepoints} timepoints in the study.
```
:::

With normal R Markdown [inline reporting](https://bookdown.org/yihui/rmarkdown-cookbook/r-code.html)
we would have written this in our `.Rmd` file instead:

````{verbatim}
The dataset contains `r nrow(Orange)` tree size measurements
from `r n_trees` trees at `r n_timepoints` time points in the study.
````

The two forms are very similar,
but the `epoxy` chunk approach provides a few advantages,
as we'll discover in this vignette.

## Collect your variables in lists

In the above example,
we used normal variables that were available in the global environment of our document.
But a small structural change can bring great benefits.
It's worth reading [Tristan's blog post][tj-lists], 
but to steal his thunder: store your data in lists.

We could, on the one hand,
create variables named `knitted_when`, `knitted_where` and `knitted_with` 
that all store facts about the knitting process.
The `knitted_` prefix is helpful as an aid to remember that these variables are related.

But you could store those three variables in a single object instead.
Bundling everything into a `list()`
allows you to report the results
by accessing the list elements by name with `$`.

```{r}
knitted <- list(
	when = format(Sys.Date()),
	where = knitr::current_input(),
	with = format(utils::packageVersion("knitr")),
	doc_url = "https://rdrr.io/pkg/knitr/man/knit.html"
)
```

````{verbatim}
```{epoxy}
Report prepared on {knitted$when} from `{knitted$where}` 
with knitr version {knitted$with} {emo_ji('happy')}. 
Read more about [`knitr::knit()`]({knitted$doc_url}).
```
````

::: epoxy-output
```{epoxy echo=FALSE}
Report prepared on {knitted$when} from `{knitted$where}` 
with knitr version {knitted$with} {emo_ji('happy')}. 
Read more about [`knitr::knit()`]({knitted$doc_url}).
```
:::

This is still essentially equivalent to R Markdown's inline R chunks.
But `epoxy` chunks include a `data` chunk argument,
which allows us to reference items in the `knitted` list
directly without having to use `$`.

````{verbatim}
```{epoxy knitted-2, data = knitted}
Report prepared on {when} from `{where}` 
with knitr version {with} {emo_ji('happy')}. 
Read more about [`knitr::knit()`]({doc_url}).
```
````

::: epoxy-output
```{epoxy knitted-2, data = knitted}
Report prepared on {when} from `{where}` 
with knitr version {with} {emo_ji('happy')}. 
Read more about [`knitr::knit()`]({doc_url}).
```
:::

Note that we can still have arbitrary R code
in epoxy inline expressions:
the `emo_ji()` function —
a vignette-safe version of `emo::ji()` —
exists in my global environment.


## Reporting Model Results

Suppose we have some model results that we've prepared into a table
(for details, see [Tristan's blog post][tj-lists]).
These results summarize a linear mixed model estimating population averages
for trees grown in several ozone conditions.
I've copied the resulting data frame into this vignette to avoid taking extra dependencies for this vignette.

```{r}
text_ready <-
	data.frame(
		term = c("intercept", "hund_days", "ozone", "hund_days_ozone"),
		estimate = c("4.25", "0.34", "&minus;0.14", "&minus;0.04"),
		se = c(0.131, 0.013, 0.158, 0.015),
		ci = c("[4.00, 4.51]", "[0.31, 0.36]", "[&minus;0.45, 0.17]","[&minus;0.07, &minus;0.01]"),
		stringsAsFactors = FALSE
	)
```

We can use `split()` to make a list of data frames that we can index by the values in the `term` column.

```{r}
stats <- split(text_ready, text_ready$term)
```

We now have a list of one-row dataframes:

```{r}
str(stats)
```

Now we can write up our results with inline reporting:

````
```{epoxy}`r ''`
`r paste(knitr::knit_code$get("stats-paragraph"), collapse = "\n")`
```
````

::: epoxy-output
```{epoxy stats-paragraph}
The average log-size in the control condition was
{stats$intercept$estimate} units, 
95% Wald CI {stats$intercept$ci}.
There was not a statistically clear difference between the 
ozone conditions for their intercepts (day-0 values), 
*B* = {stats$ozone$estimate}, {stats$ozone$ci}.
For the control group, the average growth rate was 
{stats$hund_days$estimate} log-size units per 100 days, 
{stats$hund_days$ci}. The growth rate for 
the ozone treatment group was significantly slower, 
*diff* = {stats$hund_days_ozone$estimate}, 
{stats$hund_days_ozone$ci}.
```
:::

### Inline reporting with autocomplete

What's extra neat about epoxy — 
and not readily apparent if you're reading this vignette —
is that RStudio's autocomplete feature kicks in when you type `stats$`
inside a braced expression `{ }`.

Actually,
because the IDE doesn't know about the `epoxy` knitr engine,
the autocomplete tries to help out on every word.
It's typically easy to ignore the suggestions for words that are part of the prose,
and it's usually outweighed by the usefulness of being able to autocomplete
the names in your data structures.

### Intermittent inline-reporting

Note that you don't need to write your entire document or even paragraph
inside an `epoxy` chunk;
you can wrap only the data-heavy parts as needed.

````{verbatim}
There was not a statistically clear difference between the 
ozone conditions for their intercepts (day-0 values),
```{epoxy}
*B* = {stats$ozone$estimate}, {stats$ozone$ci}.
```
The growth rate for the ozone treatment group was significantly slower,
```{epoxy}
*diff* = {stats$hund_days_ozone$estimate}, {stats$hund_days_ozone$ci}.
```
````

::: epoxy-output
There was not a statistically clear difference between the 
ozone conditions for their intercepts (day-0 values),
```{epoxy}
*B* = {stats$ozone$estimate}, {stats$ozone$ci}.
```
The growth rate for 
the ozone treatment group was significantly slower,
```{epoxy}
*diff* = {stats$hund_days_ozone$estimate}, 
{stats$hund_days_ozone$ci}.
```
:::

## Repeated inline reporting

Occasionally you may need to re-use the same phrase or document structure
but for different slices of your data.

### Vectorized inline reporting chunks

Suppose we summarize the orange tree growth
(normally I would use a combination of `dplyr::group_by()` and `dplyr::summarize()` here.)

```{r orange_summary}
summarize_tree_growth <- function(tree) {
	tree <- Orange[Orange$Tree == tree, ]
	tree <- data.frame(
		tree = tree$Tree[1],
		age_range = diff(range(tree$age)),
		circumference_first = tree$circumference[1],
		circumference_last = tree$circumference[nrow(tree)]
	)
	tree$growth_rate <- with(tree, (circumference_last - circumference_first) / age_range)
	tree
}

orange_summary <- lapply(1:5, summarize_tree_growth)
orange_summary <- do.call(rbind, orange_summary)
orange_summary
```

`epoxy` chunks, like `glue::glue()`, are vectorized,
so if we find ourselves needing to repeat the same thing over and over again,
we can use this feature to our advantage.

````{verbatim}
A quick recap of the growth observed in the orange trees:

```{epoxy data = orange_summary}
- Tree number {tree} started out at {circumference_first}mm and,
  over {age_range} days, grew to be {circumference_last}mm.
```
````

::: epoxy-output
A quick recap of the growth observed in the orange trees:

```{epoxy data = orange_summary}
- Tree number {tree} started out at {circumference_first}mm and,
  over {age_range} days, grew to be {circumference_last}mm.
```
:::

### Template inline reporting chunks

By using [knitr's reference labels feature](https://bookdown.org/yihui/rmarkdown-cookbook/reuse-chunks.html#ref-label),
and the `epoxy` `data` chunk option we saw above,
you can create an epoxy template
that you can re-use like a parameterized chunk.

You start by creating a labelled `epoxy` chunk with `eval = FALSE`

````{verbatim}
```{epoxy average-growth, eval=FALSE}
an average of {signif(growth_rate * 7, 2)}mm per week.
```
````

```{epoxy average-growth, eval=FALSE}
an average of {signif(growth_rate * 7, 2)}mm per week.
```

that you can later use in your prose 
by referencing the chunk with `ref.label`
and providing a different slice of data via the `data` chunk option.

````{verbatim}
The fourth tree was the largest tree at the end of the study, growing
```{epoxy ref.label="average-growth", data = summarize_tree_growth(4)}
```
Meanwhile, the smallest tree was the third, which grew at
```{epoxy ref.label="average-growth", data = summarize_tree_growth(3)}
```
````

::: epoxy-output
The fourth tree was the largest tree at the end of the study, growing
```{epoxy ref.label="average-growth", data = summarize_tree_growth(4)}
```
Meanwhile, the smallest tree was the third, which grew at
```{epoxy ref.label="average-growth", data = summarize_tree_growth(3)}
```
:::
