```{r airbnb-data, echo=FALSE}
# Airbnb stats that may not be completely accurate
airbnb <- list(
 countries = 220,
 cities = 1e5,
 avg_stay = 4.326,
 avg_cost = 184.952,
 hosts = 4.12e6
)
```

````markdown
```{r}`r ''`
`r paste(knitr::knit_code$get("airbnb-data"), collapse = "\n")`
```
````

With standard inline R code in R Markdown, we can write the following:

```{verbatim}
* Airbnb includes listings in `r airbnb$cities` cities
  in `r airbnb$countries` countries
  from around `r airbnb$hosts` hosts.
  The average guest stays `r airbnb$avg_stay` nights
  at a rate of `r airbnb$avg_cost` per night.
```

* Airbnb includes listings in 10^5 cities
  in `r I(airbnb$countries)` countries
  from around 4.12 × 10^6 hosts.
  The average guest stays `r airbnb$avg_stay` nights
  at a rate of `r airbnb$avg_cost` per night.

Using `epoxy` and the light-weight `fmt()` function from `epoxy_transform_format()`,
we can improve the readability and formatting of the interwoven numbers.


````markdown
```{r my_style, echo = FALSE}`r ''`
`r paste(knitr::knit_code$get("my-style"), collapse = "\n")`
```

```{epoxy .transformer = my_style}`r ''`
`r paste(knitr::knit_code$get("airbnb-epoxy"), collapse = "\n")`
```
````

```{r my-style, echo = FALSE}
# Define number/dollar format to apply consistently
my_style <- epoxy_transform_format(
 dollar = scales::label_dollar(accuracy = 1),
 number = scales::label_number(
   accuracy = 0.1,
   scale_cut = scales::cut_short_scale()
 )
)
```

```{epoxy airbnb-epoxy, .transformer = my_style}
* Airbnb includes listings in {fmt(airbnb$cities, ",")} cities
  in {fmt(airbnb$countries, "auto")} countries
  from around {fmt(airbnb$hosts, "#")} hosts.
  The average guest stays {fmt(airbnb$avg_stay, "#")} nights
  at a rate of {fmt(airbnb$avg_cost, "$")} per night.
```
