
````{verbatim}
```{r}
# Subset `airquality` dataset to May, 1973
airquality_may <- airquality[airquality$Month == 5, ]
```

```{epoxy}
The average temperature was {signif(mean(airquality_may$Temp))}
at LaGuardia Airport in New York in May of 1973.
```
````

When rendered, epoxy fills in the `{ }` for you:

```{r echo=FALSE}
glue::glue("> The average temperature was {signif(mean(airquality_may$Temp))}
at LaGuardia Airport in New York in May of 1973.")
```


To use epoxy in your R Markdown document,
create a new chunk using the engine of your choice.
In that chunk, write in markdown, HTML, or LaTeX as needed,
wrapping R expressions inside the delimiters for the epoxy chunk.

````{verbatim}
```{epoxy}
The average speed of the cars was **{mean(cars$speed)} mph.**
But on average the distance traveled was only _{mean(cars$dist)}_.
```
````

```{epoxy}
The average speed of the cars was **{mean(cars$speed)} mph**.
But on average the distance traveled was only _{mean(cars$dist)} ft_.
```

`epoxy` is built around `glue::glue()`,
so the chunk above is equivalent to the following.

```{r}
glue::glue("The average speed of the cars was **{mean(cars$speed)} mph**.
But on average the distance traveled was only _{mean(cars$dist)} ft_.")
```

One immediate advantage of using `epoxy` instead of `glue::glue()`
is that RStudio's autocompletion feature works inside `epoxy` chunks!
Typing `cars$` in the chunk will suggest the columns of `cars`.
