To change the transformer used by [epoxy()] and the HTML and LaTeX variants, use `epoxy_transform_set()`.
This function takes the same values as [epoxy_transform()], but makes them the default transformer for any [epoxy()] calls that do not specify a transformer.
By default, the setting is made for all engines, but you can specify a single engine with the `engine` argument.

Here's a small example that applies the [bold][epoxy_transform_bold] and [collapse][epoxy_transform_collapse] transformers to all epoxy chunks:

```{r eval = FALSE}
epoxy_transform_set("bold", "collapse")
```

Most often, you'll want to to update the default transformer to customize the formatting functions used by the [inline transformer][epoxy_transform_inline].
You can use `epoxy_transform_set()` to change settings of existing formatting functions or to add new one.
Pass the new function to an argument with the dot-prefixed name.

In the next example I'm setting the `.dollar` transformation to use "K" and "M" to abbreviate large numbers.
I'm also adding my own transformation that truncates long strings to fit in 8 characters.

```{r eval = FALSE}
epoxy_transform_set(
	.dollar = scales::label_dollar(
		accuracy = 0.01,
		scale_cut = scales::cut_short_scale()
	),
	.trunc8 = function(x) glue::glue_collapse(x, width = 8)
)

epoxy("{.dollar 12345678}")
#> $12.34M
epoxy("{.trunc8 12345678}")
#> 12345...
```

Note that the `engine` argument can be used even with inline tranformations, e.g. to apply a change only for HTML you can use `engine = "html"`.

To unset the session defaults, you have two options:

1. Unset everything by passing `NULL` to `epoxy_transform_set()`:

	 ```{r eval = FALSE}
	 epoxy_transform_set(NULL)
	 ```

1. Unset a single inline transformation by passing `rlang::zap()` to the named argument:

	 ```{r eval = FALSE}
	 epoxy_transform_set(.dollar = rlang::zap())
	 ```

Or you can provide new values to overwrite the current settings.
And as before, you can unset session defaults for a specific `engine`.
